hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-02-28 inst/manuscript/paper.Rmd

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(hatchR)
library(ggdist)
library(ggridges)
```

@@

@@

where $E_i$ is the effective value and $T_i$ the temperature for day $i$, and $a$ and $b$ are model parameterization estimates (i.e. species- or model-specific constants).

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse); library(hatchR); library(ggdist); library(ggridges)
```

@@

where $E_i$ is the effective value and $T_i$ the temperature for day $i$, and $a$ and $b$ are model parameterization estimates (i.e. species- or model-specific constants). A fish hatches or emerges when the cumulative sum of effective values reaches one:

$$
\sum_{i =1}^nE_i = 1
$$
